---
title: "GL networks"
date: "February 26, 2018"
output: pdf_document
---

In the current version of the paper we are using collapsed versions of the GL networks. A while ago we took this decision for two reasons:

1.  Since we are comparing 2010 to 2012, dynamics are not useful here. We just use the 2010 network compute exposures.

2.  The GL networks for the latest years are too sparse to be used in the models.

Here are a couple of visualizations of the adjacency matrices that shows the second point:

```{r Setup, echo=FALSE, message=FALSE, warning=FALSE}

knitr::opts_chunk$set(out.width = ".4\\linewidth")
# DESCRIPTION:
# This file runs linear models on then proportion of implementation using the
# co-subscription networks.

# Preparing space
options(stringsAsFactors = FALSE)

library(netdiffuseR)
library(texreg)
library(Matrix)
library(spdep)
library(AER)

model_data <- read.csv("../data/model_data.csv", na="<NA>", check.names = FALSE)
model_data <- model_data[with(model_data, order(year, entry)),]
model_data$`year2012` <- as.integer(model_data$year == 2012)
load("../data/adjmats.rda")
load("../data/adjmat_border.rda")
load("../data/adjmat_mindist.rda")
load("../data/adjmat_centroid_dist.rda")

# List of networks (with pretty names) that will be used
networks      <- c(
  "adjmat_centroid_dist", "Centroid Distance",
  "adjmat_mindist", "Minimal distance",
  "adjmat_general_trade", "General Trade",
  "adjmat_tobacco_trade", "Tobacco Trade",
  "adjmat_referrals", "GLOBALink Referrals",
  "adjmat_interest_group_comembership_twomode",
  "GLOBALink co-subscription"#,"Interest Group co-membership",
  # "adjmat_fctc_cop_coparticipation_twomode", "FCTC COP co-participation",
  # "adjmat_fctc_inb_coparticipation_twomode", "FCTC INB co-participation",
  # "adjmat_border", "Country Borders",
  # "adjmat_gl_posts", "GlobalLink Posts"
  )

```

```{r GL-posts, echo=FALSE}

image(adjmat_gl_posts$`2010`, xlab="GL Posts 2010")

# Preprocessing networks gl_posts and referrals
g0 <- adjmat_gl_posts[as.character(2008:2010)] # 
adjmat_gl_posts <- g0[[1]]
for (g in g0[-1])
  adjmat_gl_posts <- adjmat_gl_posts + g

image(adjmat_gl_posts, xlab = "GL Posts 2008-2010 collapsed")
# nlinks(adjmat_gl_posts)/(nnodes(adjmat_gl_posts)*(nnodes(adjmat_gl_posts)-1))

```


```{r GL-referals, echo=FALSE}

image(adjmat_referrals$`2010`, xlab = "GL Referals 2010")

g0 <- adjmat_referrals # 
adjmat_referrals <- g0[[1]]
for (g in g0[-1])
  adjmat_referrals <- adjmat_referrals + g

image(adjmat_referrals, xlab="GL Referals 2002-2011 collapsed")

```


```{r GL-co-subscriptions, echo=FALSE}

image(adjmat_interest_group_comembership_twomode$`2010`, xlab = "GLOBALink co-subscription 2010")

```

